\documentclass{article}
\usepackage{amsmath, fullpage}
\usepackage{graphicx}
\usepackage{float}

\title{6.170 Final Project Team Contract}
\date{November 05, 2013}
\author{Naim Luj$\acute{a}$n, Dwyane George, Deborah Chen, Yi-Shiuan Tung}

\begin{document}

\maketitle{}

\section*{Personal Goals}
\begin{itemize}
\item Apply 6.170 principles to build cool and useful product.
\item Do well on the project and get A's.
\item Be able to communicate openly to resolve any issues that may arise with project.
\end{itemize}

\section*{Expected level of achievement and effort}
\begin{itemize}
\item Each member is committed to delivering the final product, and will put in the required effort.
\item Each member will participate in every aspect of the project, including design, coding, and testing.
\item Members will meet their assigned deadlines and attend the weekly meetings to discuss progress.
\end{itemize}

\section*{Frequency, length and location of team meetings}
\begin{itemize}
\item Team meetings will be every Wednesday at 5pm. We will use this time to integrate our work, discuss the project and assign tasks.
\item On Saturdays at 2pm, we'll meet up and code together.
\item We will have weekly consultations with our assigned teaching assistant to get feedback on our design and implementation approach.
\item We will be on time, and let team members know ahead of time (at least a day for TA meetings, couple hours for our own meetings) if we can’t make it/will be late. 
\end{itemize}

\section*{How quality of work will be maintained}
\begin{itemize}
\item Each member will demonstrate their work to the group during meetings.
\item Code will be reviewed by at least one other member of the team.
\item Make sure no one works on the same thing and there is clear communication on workflow.
\item If we notice issues with quality of work, we will bring it up and work to fix the problem.
\end{itemize}

\section*{How tasks will be assigned, and what to do if deadlines are missed}
\begin{itemize}
\item Every attempt will be made to assign tasks based on team member’s preference.
\item Work will be split fairly and evenly across all team members.
\item Notify the group ahead of time if you’ll be having a difficult week. The team will support you and figure out a plan to help you/re-divide work to make sure it gets done
\item We will set our own milestones ahead of the class timeline. At each team meeting, agree on what will be done by next meeting. 
\end{itemize}

\section*{How decisions will be made and disagreements resolved}
\begin{itemize}
\item Try to come to consensus. If necessary, take a majority vote after thorough discussion.
\item We will consult the TAs if we want other perspectives on issues.
\item Disagreements should not be personal, but about the project.
\end{itemize}

\end{document}